\documentclass[12pt]{article}

\usepackage{fancyhdr}
\usepackage{fullpage}
\usepackage{hyperref}
\usepackage[table]{xcolor}
\usepackage[font=scriptsize]{caption}
\usepackage[pdftex]{graphicx}
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\usepackage[UKenglish]{isodate}% http://ctan.org/pkg/isodate
\usepackage {tabularx}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{changepage}% http://ctan.org/pkg/changepage
\usepackage{pdfpages}
\usepackage{enumitem}
\usepackage{tikz}
\usepackage{tikz-uml}
\usetikzlibrary{arrows,shadows,positioning}
\usetikzlibrary{shadows.blur}
\usetikzlibrary{shapes.symbols}
\usepackage{tocloft}
\usepackage{pgf-umlsd}
\usepackage{ifthen}
\usepackage{xstring}
\usepackage{pgfopts}
\usepackage{calc}
\usepackage{babel}

\pagestyle{fancy}

\headheight = 28pt 
\headsep = 12pt
\cleanlookdateon
\fancyhead[L]{CEN4020\\FALL2014}
\fancyhead[C]{Software Engineering I\\\today}
\fancyhead[R]{Prestige Worldwide\\Prospectus}

\fancyfoot[C]{}
\fancyfoot[R]{\thepage { $|$ Page}}

\definecolor{light-gray}{gray}{0.90}
\definecolor{dark-gray}{gray}{.65}

\setlength{\parindent}{1cm} % Default is 15pt.

\pagenumbering{roman}

\setcounter{secnumdepth}{0}

% Table of contents dots
\renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}}
\begin{document}
  \input{./title.tex}

  \tableofcontents
  %\listoffigures

  \clearpage

  % reset page numbering
  \pagenumbering{arabic}
  \setcounter{page}{1}

  \section{Roles and Responsibilities}
  %\begin{adjustwidth}{2.5em}{0pt}
  %  \footnotesize{Software Engineering 9th Edition, Ian Sommerville, page 78}\\
  %\end{adjustwidth}
  \begin{adjustwidth}{1.5em}{0pt}
    \begin{itemize}
      \item Project Manager (Arron Solano): Responsible for ensuring that tasks related to completing our project will be completed in a timely and correct manner. Daily and weekly meetings will be held to enhance the work done by the project manager.
      \item Front End \& User Interface Developer (Brian Howell): Responsible for development and implementation of user interfaces.
      \item Back End Developer (Daniel Carroll): Responsible for developing database storage system and other functions related to storage and application functionality.
       \item Bitcoin Integration (Michael Danko): Responsible for integrating software functions to work in conjunction with bitcoin blockchain.
    \end{itemize}
    
\end{adjustwidth}

  \section{Project Description}
  \begin{adjustwidth}{1.5em}{0pt}

  \normalsize{Bitcoin WalleTx is a bitcoin wallet tracker tool for Android that assists users in monitoring their bitcoin balance, transaction history, and spending trends across multiple wallets. It is common for bitcoin users to possess numerous wallets, yet there do not exist many services that are capable of aggregating wallet information in order to provide the user with an overall picture of their bitcoin savings and expenditures. Bitcoin WalleTx solves this problem by allowing users to group or categorize their bitcoin wallets, as well as tag their transactions with real-world information related to how their bitcoins are being spent. Charts and graphs help to identify trends in both single wallet spending and across wallet groups, a useful feature that is essential for enabling users to integrate their bitcoin finances with a more traditional budget.}\\

  \normalsize{Bitcoin WalleTx is targeted toward all bitcoin users, as it is useful for identifying trends regardless of the number of wallets held. The average person is more concerned with budgeting than with hashes and confirmation numbers, and transaction tagging will enable users to identify trends in their spending. The concept of financial trackers has been extremely successful outside of the bitcoin space with services like Mint.com, and Bitcoin WalleTx aims to bring some of these needed features to bitcoin.}\\
  \end{adjustwidth}

  \normalsize{The project scope shall include the ability to:}\\ 
  
  \begin{adjustwidth}{1.5em}{0pt}
    \begin{itemize}
      \item Import \& delete public keys for balance\textbackslash{transaction} tracking
      \item Define \& delete wallet groups
      \item Group public keys based on user preference
      \item Define \& delete transaction tags
      \item Tag transactions
      \item View single wallet (or group) balance \& transaction summaries
      \item View single wallet (or group) balance \& transactions detail view
      \item View single wallet (or group) balance \& transactions graphical views
      \item View single wallet (or group) transaction trends using tags
      \item View transactions details

    \end{itemize}
  \end{adjustwidth}

  \section{Software Competitors}
  \begin{adjustwidth}{1.5em}{0pt}

  \normalsize{Numerous services exist, such as Bitcoin Balance for Android, that allow users to monitor a wallet's balance and transactions; however, very few services allow the user to
  group wallets and view aggregated totals related to multiple wallets. While this feature alone puts Bitcoin WalleTx ahead of most other bitcoin wallet tracking services, no other 
  services could be located that allow for transaction tagging. Instead, transaction details provided by competitor services are all related to the Blockchain and provide no useful 
  information regarding the actual real-world purpose of a transaction. }\\ 
  \end{adjustwidth}

\end{document}
