\section{Appendices}
  \subsection{Data Dictionary}
    \subsubsection{Actor Descriptions}
	Actor Descriptions 

Identifying actors:
*Who will supply, use, or remove information from the system?
*Who will use the system?
*Who is interested in a certain feature or service provided by the system?
*Who will support and maintain the system?
*What are the system's external resources?
*What other systems will need to interact with the system under development?

Actors will be the customer/user of the application.  Most interested in our application would be those interested in Bitcoin. Service and maintenance of the system will be performed by the developers(Prestige Worldwide). Systems external resources will be blockchain, SQLite, and other external wallets providing information. (Michael and Brian please confirm external resources of Bitcoin)


    \subsubsection{Use Case Descriptions}
	Use Case Descriptions

Identifying use cases:
*What are the goals that the actor will attempt to accomplish with the system?
*What are the primary tasks that the actor wants the system to perform?
*Will the actor create, store, change, remove, or read data in the system?
*Will the actor need to inform the system about sudden external changes?
*Does the actor need to be informed about certain occurrences, such as unavailability of a network resource, in the system?
*Will the actor perform a system startup or shutdown?

Use cases will be outlined in diagrams provided. 
The primary task of the customer/user will be to interact with the application.  Their main purpose will be to monitor their bitcoin currency from multiple wallets and tag transactions to better organize all transactions.  The actor will have the ability to add and remove wallets/add and remove tags pertaining to transactions. The actor can observe aggregate information in the form of graphs, charts, etc.  The actor will be alerted to certain trigger events. (updated wallet info, specific transactions, etc).  The actor has the ability to close and open application in running OS and also has the ability to completely remove the application from existing OS. 
	
	
    \subsubsection{Class Descriptions}
    \subsubsection{Attribute Descriptions}
  \subsection{Raw Use Case Point Analysis}
    \subsubsection{Actor Summary Table}
    \subsubsection{Use Case Summary Table}
    \subsubsection{Screens and Reports with Navigation Matrix}
  \subsection{Other Appendices}
